---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# syn

The goal of syn is to provide two main functions:

- `syn`, which generates synonyms
- `ant`, which generates antonyms

Currently only `syn` is working, `ant`, will be developed in the future.

## Synonyms for "cool"

The `syn` function returns all synonyms for a given word.

Let's look at synonyms for "cool":

```{r example, message = FALSE, warnings = FALSE}
library(syn)

syn_cool <- syn("cool")

head(syn_cool)
tail(syn_cool)
```

Wow, there are a lot! How many are there?

```{r length-syn-cool}
length(syn_cool)
```

Wow! There are `r length(syn_cool)` synonyms for cool. That's...`r syn("cool", 1)`, I guess.

## Set the number of words to return

You can also provide it a number of words to return with the `n_words` argument, which will randomly select the number of words given

```{r syn-awesome-one}
syn("awesome", 1)
syn("awesome", 2)
syn("awesome", 5)
```

OK cool, let's use these in a sentence, using the `glue` package. 

## Example: Creating a sentence

Which of these better?

```{r example-syn-glue}

glue::glue("This is really cool!")
glue::glue("This is really {syn('cool', 1)}!")
glue::glue("This is really {syn('cool', 10)}!")
```

## Using multiple words

You can generate synonyms for multiple words with the `syns` function. This takes a vector of words, returning a named list

```{r example-syns}
syns_good_evil <- syns(c("good", "evil"))
str(syns_good_evil)
```

You can also provide `n_words` for `syns`, and it will return a random number of the words.

```{r syns-n-words}
syns(c("good", "evil"),
     n_words =  10)
```

